---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document
---


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Selectivity and Retention {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Selectivity and Retention')
}

dd <- Pars$M_ageArray %>% dim()
nsim <- dd[1]
maxage <- dd[2]

nsamp <- length(its)
```

### Sampled Selectivity Parameters
Histograms of `r nsim` simulations of length at 5% selection (`L5`), first length at full selection (`LFS`), and vulnerability of animals at mean asymptotic length (`Vmaxlen`) for the first historical year, the last historical year, and the last projection year, wtih vertical colored lines indicating `r nsamp` randomly drawn values used in the other plots:

```{r, echo=FALSE}
par(mfrow=c(3,3), oma=c(0,0,3,0), mar=c(2,1,3,1))

Yr <- 1
hist2(Pars$L5[1,], col=plotPars$col, axes=plotPars$axes, main="L5", breaks=plotPars$breaks)
abline(v=Pars$L5[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFS[1,], col=plotPars$col, axes=plotPars$axes, main="LFS", breaks=plotPars$breaks)
abline(v=Pars$LFS[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
mtext(side=3, "First Historical Year", xpd=NA)

hist2(Pars$Vmaxlen[1,], col=plotPars$col, axes=plotPars$axes, main="Vmaxlen", breaks=plotPars$breaks)
abline(v=Pars$Vmaxlen[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

Yr <- nyears
hist2(Pars$L5[1,], col=plotPars$col, axes=plotPars$axes, main="L5", breaks=plotPars$breaks)
abline(v=Pars$L5[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFS[1,], col=plotPars$col, axes=plotPars$axes, main="LFS", breaks=plotPars$breaks)
abline(v=Pars$LFS[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
mtext(side=3, "Last Historical Year", xpd=NA)

hist2(Pars$Vmaxlen[1,], col=plotPars$col, axes=plotPars$axes, main="Vmaxlen", breaks=plotPars$breaks)
abline(v=Pars$Vmaxlen[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

Yr <- nyears + proyears
hist2(Pars$L5[1,], col=plotPars$col, axes=plotPars$axes, main="L5", breaks=plotPars$breaks)
abline(v=Pars$L5[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFS[1,], col=plotPars$col, axes=plotPars$axes, main="LFS", breaks=plotPars$breaks)
abline(v=Pars$LFS[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
mtext(side=3, "Last Projection Year", xpd=NA)

hist2(Pars$Vmaxlen[1,], col=plotPars$col, axes=plotPars$axes, main="Vmaxlen", breaks=plotPars$breaks)
abline(v=Pars$Vmaxlen[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

```

### Sampled Retention Parameters

Histograms of `r nsim` simulations of length at 5% retention (`LR5`), first length at full retention (`LFR`), and retention of animals at mean asymptotic length (`Rmaxlen`) for the first historical year, the last historical year, and the last projection year, wtih vertical colored lines indicating `r nsamp` randomly drawn values used in the other plots:

```{r, echo=FALSE}
par(mfrow=c(3,3), oma=c(0,0,3,0), mar=c(2,1,3,1))

Yr <- 1
hist2(Pars$LR5[1,], col=plotPars$col, axes=plotPars$axes, main="LR5", breaks=plotPars$breaks)
abline(v=Pars$LR5[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFR[1,], col=plotPars$col, axes=plotPars$axes, main="LFR", breaks=plotPars$breaks)
abline(v=Pars$LFR[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
mtext(side=3, "First Historical Year", xpd=NA)

hist2(Pars$Rmaxlen[1,], col=plotPars$col, axes=plotPars$axes, main="Rmaxlen", breaks=plotPars$breaks)
abline(v=Pars$Rmaxlen[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

Yr <- nyears
hist2(Pars$LR5[1,], col=plotPars$col, axes=plotPars$axes, main="LR5", breaks=plotPars$breaks)
abline(v=Pars$LR5[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFR[1,], col=plotPars$col, axes=plotPars$axes, main="LFR", breaks=plotPars$breaks)
abline(v=Pars$LFR[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
mtext(side=3, "Last Historical Year", xpd=NA)

hist2(Pars$Rmaxlen[1,], col=plotPars$col, axes=plotPars$axes, main="Rmaxlen", breaks=plotPars$breaks)
abline(v=Pars$Rmaxlen[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

Yr <- nyears + proyears
hist2(Pars$LR5[1,], col=plotPars$col, axes=plotPars$axes, main="LR5", breaks=plotPars$breaks)
abline(v=Pars$LR5[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFR[1,], col=plotPars$col, axes=plotPars$axes, main="LFR", breaks=plotPars$breaks)
abline(v=Pars$LFR[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
mtext(side=3, "Last Projection Year", xpd=NA)

hist2(Pars$Rmaxlen[1,], col=plotPars$col, axes=plotPars$axes, main="Rmaxlen", breaks=plotPars$breaks)
abline(v=Pars$Rmaxlen[1,its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

```

### Selectivity & Retention at Length

```{r, echo=FALSE}
par(mfrow=c(3,3), oma=c(3,3,1,1), mar=c(1,1,1,1))

yr.vert <- c(1, nyears, nyears+proyears)
YrText <- list()
YrText[yr.vert[1]] <- "First Historical Year"
YrText[yr.vert[2]] <- "Last Historical Year"
YrText[yr.vert[3]] <- "Last Projection Year"
cnt <- 0 
for (sim in its) {
   cnt <- cnt + 1
  for (yr in yr.vert) {
   
    # plot vulnerability & selection at length
    plot(Pars$CAL_binsmid, Pars$SLarray2[sim,, yr], type='l', ylim=c(0,1), lwd=plotPars$lwd, 
         axes=FALSE, ylab="", xlab="")
    if (sim == its[1]) {
      mtext(side=3, YrText[[yr]])
    }
    if (sim == its[length(its)]) {
      axis(side=1)
    } else {
       axis(side=1, labels = FALSE)
    }
    if (sim == its[nsamp]) mtext(side=1, "Length", line=2.5)
    if (yr == yr.vert[1] & sim ==its[1]) {
      mtext(side=2, "Vulnerability/Retention", las=3, outer=TRUE, line=2)
    }
    if (yr == yr.vert[1]) {
       text(Pars$CAL_binsmid[1], 1, "Simulation", xpd=NA, col=cnt, pos=4)
      axis(side=2)
    }
    if (yr != yr.vert[1]) axis(side=2, labels=FALSE)
    
    polygon(x=c(Pars$CAL_binsmid, rev(Pars$CAL_binsmid)), 
            y=c(Pars$SLarray[sim,, yr], rev(Pars$retL[sim,, yr])), col="gray", border=FALSE)
    lines(Pars$CAL_binsmid, Pars$SLarray[sim,, yr], col=2, lwd=plotPars$lwd, lty=2, type='l')
    lines(Pars$CAL_binsmid, Pars$retL[sim,, yr], col=4, lwd=plotPars$lwd, lty=3, type='l')
    
    if (yr == max(yr.vert) & sim == its[1]) {
      minval <- min(c(Pars$V[sim,Pars$maxage, yr],  Pars$retA[sim,Pars$maxage, yr]))
      if (minval >= 0.5) loc <- "bottomright"
      if (minval < 0.5) loc <- "topright"
      legend(loc, legend = c("Vulnerability", "Realized Selection", "Retention"),
             lwd=2, col=c(1, 2, 4), bty="n", lty=c(1,2,3))
    }
  }
}

```

### Selectivity & Retention at Age
```{r, echo=FALSE}
par(mfrow=c(3,3), oma=c(3,3,1,1), mar=c(1,1,1,1))

yr.vert <- c(1, nyears, nyears+proyears)
YrText <- list()
YrText[yr.vert[1]] <- "First Historical Year"
YrText[yr.vert[2]] <- "Last Historical Year"
YrText[yr.vert[3]] <- "Last Projection Year"
cnt <- 0 
for (sim in its) {
   cnt <- cnt + 1
  for (yr in yr.vert) {
   
    # plot vulnerability & selection at length
    plot(1:Pars$maxage, Pars$V2[sim,, yr], type='l', ylim=c(0,1), lwd=plotPars$lwd, 
         axes=FALSE, ylab="", xlab="")
    if (sim == its[1]) {
      mtext(side=3, YrText[[yr]])
    }
    if (sim == its[length(its)]) {
      axis(side=1)
    } else {
       axis(side=1, labels = FALSE)
    }
    if (sim == its[nsamp]) mtext(side=1, "Age", line=2.5)
    if (yr == yr.vert[1] & sim ==its[1]) {
      mtext(side=2, "Vulnerability/Retention", las=3, outer=TRUE, line=2)
    }
    if (yr == yr.vert[1]) {
       text(1, 1, "Simulation", xpd=NA, col=cnt, pos=4)
      axis(side=2)
    }
    if (yr != yr.vert[1]) axis(side=2, labels=FALSE)
    
    polygon(x=c(1:Pars$maxage, rev(1:Pars$maxage)), 
            y=c(Pars$V[sim,, yr], rev(Pars$retA[sim,, yr])), col="gray", border=FALSE)
    lines(1:Pars$maxage, Pars$V[sim,, yr], col=2, lwd=plotPars$lwd, lty=2, type='l')
    lines(1:Pars$maxage, Pars$retA[sim,, yr], col=4, lwd=plotPars$lwd, lty=3, type='l')
    
    if (yr == max(yr.vert) & sim == its[1]) {
      minval <- min(c(Pars$V[sim,Pars$maxage, yr],  Pars$retA[sim,Pars$maxage, yr]))
      if (minval >= 0.5) loc <- "bottomright"
      if (minval < 0.5) loc <- "topright"
      legend(loc, legend = c("Vulnerability", "Realized Selection", "Retention"),
             lwd=2, col=c(1, 2, 4), bty="n", lty=c(1,2,3))
    }
  }
}
```


