---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document
---

```{r, echo=FALSE, results="asis"}
suppressMessages(library(dplyr))
if (params$tabs) {
  cat('## Natural Mortality Parameters {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Natural Mortality Parameters')
}

dd <- Pars$M_ageArray %>% dim()
nsim <- dd[1]
maxage <- dd[2]

nsamp <- length(params$its)

```



### Sampled Parameters 
Histograms of `r nsim` simulations of `M`, `Mexp`, and `Msd` parameters, with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r M_samples, echo=FALSE}
par(mfrow=c(1,3))
hist2(Pars$M, main="M", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$M[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Mexp, main="Mexp", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Mexp[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 

hist2(Pars$Msd, main="Msd", col=params$plotPars$col, axes=params$plotPars$axes,
      breaks=params$plotPars$breaks, cex.main=params$plotPars$cex.main)
abline(v=Pars$Msd[params$its], col=1:nsamp, lwd=params$plotPars$lwd)
axis(side=1) 
```


### Time-Series
The average natural mortality rate by year for adult fish for `r nsamp` simulations. The vertical dashed line indicates the end of the historical period:

```{r, echo=FALSE}
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
matplot(years, t(Pars$Marray[params$its,]), type="l", lty=1, bty="l", main="M by Year", 
         lwd=params$plotPars$lwd, ylab="M", xlab="Years", las=1)
abline(v=0, col="darkgray", lty=2)
```



### M-at-Age 
Natural mortality-at-age for `r nsamp` simulations in the first historical year, the last historical year (i.e., current year), 
and the last projected year:

```{r, echo=FALSE}
par(mfrow=c(1,3))
lims <- range(Pars$M_ageArray[params$its,, ])
ylab <- "Natural Mortality"
matplot(t(Pars$M_ageArray[params$its,,1]), type="l", lty=1, bty="l", 
        lwd=params$plotPars$lwd, ylim=lims, ylab=ylab, las=1)
mtext(side=3, "First historical year", cex=0.8, line=-1)
mtext(side=1, "Age", line=2, cex=0.7)

matplot(t(Pars$M_ageArray[params$its,,nyears]), type="l", lty=1, bty="l", 
        main="M-at-age", lwd=params$plotPars$lwd, ylim=lims, axes=FALSE,
        ylab="")
mtext(side=3, "Last historical year", cex=0.8, line=-1)
axis(side=1)
mtext(side=1, "Age", line=2, cex=0.7)
matplot(t(Pars$M_ageArray[params$its,,nyears+proyears]), type="l", lty=1, 
        bty="l", lwd=params$plotPars$lwd, ylim=lims, axes=FALSE,
        ylab="")
mtext(side=3, "Last projected year", cex=0.8, line=-1)
axis(side=1)
mtext(side=1, "Age", line=2, cex=0.7)


```

### M-at-Length
Natural mortality-at-length for `r nsamp` simulations in the first historical year, the last historical year (i.e., current year), 
and the last projected year:

```{r, echo=FALSE}
par(mfrow=c(1,3))
lims <- range(Pars$M_ageArray[params$its,, ])
xlims <- range(Pars$Len_age[params$its,,])
matplot(t(Pars$Len_age[params$its,,1]), t(Pars$M_ageArray[params$its,,1]), type="l", 
        lty=1, bty="l", lwd=params$plotPars$lwd, ylim=lims, xlim=xlims, ylab="Natural Mortality", 
        xlab="", las=1)
mtext(side=3, "First historical year", cex=0.8, line=-1)
mtext(side=1, "Length", line=2, cex=0.7)
  
matplot(t(Pars$Len_age[params$its,,nyears]), t(Pars$M_ageArray[params$its,,nyears]), 
        type="l", lty=1, bty="l", main="M-at-length", lwd=params$plotPars$lwd, ylim=lims, 
        xlim=xlims, axes=FALSE, ylab="", xlab="")
axis(side=1)
mtext(side=1, "Length", line=2, cex=0.7)
mtext(side=3, "Last historical year", cex=0.8, line=-1)

matplot(t(Pars$Len_age[params$its,,nyears+proyears]), 
        t(Pars$M_ageArray[params$its,,nyears+proyears]), 
        type="l", lty=1, bty="l", lwd=params$plotPars$lwd, ylim=lims, 
        axes=FALSE, xlim=xlims, ylab="", xlab="")

mtext(side=3, "Last projected year", cex=0.8, line=-1)
axis(side=1)
mtext(side=1, "Length", line=2, cex=0.7)
  ```

