---
title: "`r params$title`"
subtitle: "`r params$subtitle`"
author: "`r params$author`"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true    
runtime: shiny   
---


<style type="text/css">

body{ /* Normal  */
   font-size: 16px;
}
td {  /* Table  */
   font-size: 16px;
}
title { /* title */
 font-size: 26px;
}
h1 { /* Header 1 */
 font-size: 24px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 21px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 19px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 16px;
}
pre { /* Code block */
  font-size: 16px
}
</style>




```{r set options, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
knitr::opts_chunk$set(dpi=85)
#options(width = 650)
```

<br>


# About this document

This is a prototype of an automatic report that describes the results of a demonstration MSE analysis for the Canadian Department of Fisheries and Oceans. 

<br>

# Quantile plot

The quantile worm plots show the central 80% probability interval of future projections (blue shaded area) and the mean among all simulations (solid white line). 

Superimposed on each plot are two individual simulations (the solid and dashed blue lines). For each management procedure (panel columns) the biomass relative to BMSY and the yield relative to FMSY yield (Rel. Yd.) are plotted. 

```{r Quantile plot,echo=F,warning=F,error=F,message=F,fig.width=8,fig.height=6}

 DFO_quant(params$MSEobj,maxcol=4)

```

<br>


# Bar plot 

The bar plots is similar to the quantile plot above and shows the biomass relative to BMSY over projected time periord. Each panel represents a different 10 year period of the MSE projection. The bars present the 90% and the 50% (solid line) probability intervals. The dots are the median biomass / BMSY. 

```{r bar,echo=F,warning=F,error=F,message=F,fig.height=10,fig.width=7}
 DFO_bar(params$MSEobj)

```

<br>


# Tradeoff plot

A traditional KOBE plot is provided that shows stock status (B/BMSY) and exploitation rate (F/FMSY) at the end of the projected time period. The dots represent individual simulations, the solid line is the 50% probability interval and the dashed line is the 95% probability interval. 


```{r TO,echo=F,warning=F,error=F,message=F,fig.height=10,fig.width=6}
 DFO_proj(params$MSEobj,maxplot=9)

```


<br>


# Version Notes

This report is subject to ongoing testing. If you find a bug or a problem please send a report to <t.carruthers@oceans.ubc.ca> so that it can be fixed or report an issue at www.github.com/DLMtool/DLMtool/issues.  

