---
params: 
    title: ""
    Pars: "`r list()`"
    plotPars: "`r list()`"
    tabs: "`r TRUE`"
    its: " `r numeric()`"
    nyears: " `r numeric()`"
    proyears: " `r numeric()`"
    date: "`r Sys.Date()`"
title: "`r params$title`"
date: "`r params$date`"
output:
  html_document:
    toc: true
    toc_float: true
---

# Observation Parameters
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Catch Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Catch Observations')
}

nsim <- Pars$Csd %>% length()

ErrList <- list()
ErrList$Cbiasa <- array(Pars$Cbias, c(nsim, nyears + proyears))  # Catch bias array
 
# composite of bias and observation error
ErrList$Cerr <- array(rlnorm((nyears + proyears) * nsim, 
                     mconv(1, rep(Pars$Csd, (nyears + proyears))), 
                     sdconv(1, rep(Pars$Csd, nyears + proyears))), 
              c(nsim, nyears + proyears))  
# Index error
ErrList$Ierr <- array(rlnorm((nyears + proyears) * nsim, 
                     mconv(1, rep(Pars$Isd, nyears + proyears)), 
                     sdconv(1, rep(Pars$Isd, nyears + proyears))), 
              c(nsim, nyears + proyears))

# Simulate error in observed recruitment index 
ErrList$Recerr <- array(rlnorm((nyears + proyears) * nsim, 
                               mconv(1, rep(Pars$Recsd, (nyears + proyears))),
                               sdconv(1, rep(Pars$Recsd, nyears + proyears))),
                        c(nsim, nyears + proyears))
  
# Simulate error in observed depletion 
ErrList$Derr <- array(rlnorm((nyears + proyears) * nsim, 
                               mconv(1, rep(Pars$Derr, (nyears + proyears))),
                               sdconv(1, rep(Pars$Derr, nyears + proyears))),
                        c(nsim, nyears + proyears))
ErrList$Dbiasa <- array(Pars$Dbias, c(nsim, nyears + proyears))  # Catch bias array

# Simulate error in observed abundance 
ErrList$Aerr <- array(rlnorm((nyears + proyears) * nsim, 
                               mconv(1, rep(Pars$Aerr, (nyears + proyears))),
                               sdconv(1, rep(Pars$Aerr, nyears + proyears))),
                        c(nsim, nyears + proyears))
ErrList$Abiasa <- array(Pars$Abias, c(nsim, nyears + proyears))  # Catch bias array

```


### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in catch observations (`Csd`) and persistent bias in observed catch (`Cbias`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Csd, main="Csd", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Csd[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$Cbias, main="Cbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Cbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

```

### Time-Series

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(ErrList$Cbiasa[its, ] * ErrList$Cerr[its, ]))
matplot(years, t(ErrList$Cbiasa[its, ] * ErrList$Cerr[its, ]),
        type="l", lty=1, bty="l", main="Catch discrepancy by Year", 
         lwd=plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Depletion Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Depletion Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in depletion observations (`Dobs`) and persistent bias in observed depletion (`Dbias`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:


```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Derr, main="Dobs", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Derr[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$Dbias, main="Dbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Dbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 



```

### Time-Series

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(ErrList$Dbiasa[its, ] * ErrList$Derr[its, ]))
matplot(years, t(ErrList$Dbiasa[its, ] * ErrList$Derr[its, ]),
        type="l", lty=1, bty="l", main="Depletion discrepancy by Year", 
         lwd=plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```




```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Abundance Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Abundance Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in abundance observations (`Btobs`) and persistent bias in observed abundance (`Btbias`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Aerr, main="Btobs", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Aerr[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$Abias, main="Btbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Abias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

```

### Time-Series

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(ErrList$Abiasa[its, ] * ErrList$Aerr[its, ]))
matplot(years, t(ErrList$Abiasa[its, ] * ErrList$Aerr[its, ]),
        type="l", lty=1, bty="l", main="Abundance discrepancy by Year", 
         lwd=plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```




```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Index Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Index Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in index observations (`Iobs`) and hyper-stability/depletion in observed index (`beta`), with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist2(Pars$Isd, main="Iobs", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Isd[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$betas, main="beta", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$betas[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

```

### Time-Series
Time-series plot of `r nsamp` samples of index observation error:
```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(4,1,3,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(ErrList$Ierr[its, ]))
matplot(years, t(ErrList$Ierr[its, ]),
        type="l", lty=1, bty="l", main="Index observation error by Year", 
         lwd=plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```

Plot showing an example true abundance index (blue) with `r nsamp` samples of index observation error and the hyper-stability/depletion parameter (`beta`):
```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(4,1,3,1))
ind<-seq(1,0.1,length.out=nyears)

Imu<-array(rep(ind,each=nsamp)^rep(Pars$betas[its],nyears),
           c(nsamp,nyears))*ErrList$Ierr[its, 1:nyears]
Imu<-Imu/apply(Imu,1,mean)
ind <- ind/mean(ind)

ylim <- range(c(ind,Imu))
plot(1:nyears, ind, type="l", ylim=ylim, bty="l", las=1, xlab="Years", 
     ylab="Relative Abundance", lwd=2, col="blue", xpd=NA,
     main="Observed Index with beta parameter")
matplot(t(Imu), add=TRUE, type="l", lwd=plotPars$lwd)
legend("topright", bty="n", col=c("blue", 1:nsamp), lwd=plotPars$lwd, 
       legend=c("True Index", paste0("Observed", 1:nsamp, sep=" ")), lty=c(1, 1:nsamp))
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Recruitment Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Recruitment Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of inter-annual variability in index observations (`Recsd`) , with vertical colored lines indicating `r nsamp` randomly drawn values used in other plots:

```{r, echo=FALSE}
par(mfrow=c(1,1))
hist2(Pars$Recsd, main="Recsd", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Recsd[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 
```

<!-- # to add hbiascv -->

### Time-Series

```{r, echo=FALSE}
par(mfrow=c(1,1), oma=c(3,3,1,1), mar=c(1,1,1,1))
years <- c(seq(-nyears+1, 0, by=1), seq(1, proyears,1))
ylim <- c(0, max(ErrList$Recerr[its, ]))
matplot(years, t(ErrList$Recerr[its, ]),
        type="l", lty=1, bty="l", main="Recruitment index discrepancy by Year", 
         lwd=plotPars$lwd, ylab="Observed/Real", xlab="Years", las=1, xpd=NA,
        ylim=ylim)
abline(v=0, col="darkgray", lty=2)
abline(h=1, col="darkgray", lty=2)
```



```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Composition Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Composition Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of catch-at-age effective sample size (`CAA_ESS`) and sample size (`CAA_nsamp`) and catch-at-length effective (`CAL_ESS`) and actual sample size (`CAL_nsamp`) with vertical colored lines indicating `r nsamp` randomly drawn values:

```{r, echo=FALSE}
par(mfrow=c(2,2))
hist2(Pars$CAA_ESS, main="CAA_ESS", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$CAA_ESS[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$CAA_nsamp, main="CAA_nsamp", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$CAA_nsamp[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1)

hist2(Pars$CAL_ESS, main="CAL_ESS", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$CAL_ESS[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$CAL_nsamp, main="CAL_nsamp", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$CAL_nsamp[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1)
```


```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Parameter Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Parameter Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of bias in observed natural mortality (`Mbias`), von Bertalanffy growth function parameters (`Linfbias`, `Kbias`, and `t0bias`), length-at-maturity (`lenMbias`), and bias in observed length at first capture (`LFCbias`) and first length at full capture (`LFSbias`) with vertical colored lines indicating `r nsamp` randomly drawn values:

```{r, echo=FALSE}
par(mfrow=c(2,2))
hist2(Pars$Mbias, main="Mbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Mbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1)

hist2(Pars$Linfbias, main="Linfbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Linfbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$Kbias, main="Kbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Kbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$t0bias, main="t0bias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$t0bias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

par(mfrow=c(1,3))
hist2(Pars$lenMbias, main="lenMbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$lenMbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFCbias, main="LFCbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$LFCbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$LFSbias, main="LFSbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$LFSbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

```



```{r, echo=FALSE, results="asis"}
if (params$tabs) {
  cat('## Reference Point Observations {.tabset .tabset-fade .tabset-pills}' )
} else {
  cat('## Reference Point Observations')
}
```

### Sampled Parameters
Histograms of `r nsim` simulations of bias in observed FMSY/M (`FMSY_Mbias`), BMSY/B0 (`BMSY_B0bias`), reference index (`Irefbias`), reference abundance (`Brefbias`) and reference catch (`Crefbias`), with vertical colored lines indicating `r nsamp` randomly drawn values:


```{r, echo=FALSE}
par(mfrow=c(2,3))
hist2(Pars$FMSY_Mbias, main="FMSY_Mbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$FMSY_Mbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1)

hist2(Pars$BMSY_B0bias, main="BMSY_B0bias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$BMSY_B0bias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$Irefbias, main="Irefbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Irefbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 

hist2(Pars$Brefbias, main="Brefbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Brefbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 


hist2(Pars$Crefbias, main="Crefbias", col=plotPars$col, axes=plotPars$axes,
      breaks=plotPars$breaks, cex.main=plotPars$cex.main)
abline(v=Pars$Crefbias[its], col=1:nsamp, lwd=plotPars$lwd)
axis(side=1) 


```


